SPIE journal papers: sample manuscript showing style and formatting specifications

### 2019-01-23 cikk/main/article.tex
file in ok

\begin{abstract}
This document shows the required format and appearance of a manuscript prepared for SPIE journals. It is prepared using LaTeX2e with the class file \texttt{spieman.cls}. The abstract should consist of a single paragraph containing no more than 200 words. It should be a summary of the paper and not an introduction. Because the abstract may be used in abstracting and indexing databases, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. A list of up to eight keywords should immediately follow, with the keywords separated by commas and ending with a period. The body of the manuscript should be double-spaced and fully justified.   
\end{abstract}

% Include a list of up to six keywords after the abstract
\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}

@@

\section{Introduction}
\label{sect:intro}  % \label{} allows reference to this section
This document shows the format and appearance of a manuscript prepared for submission to an SPIE journal. Note that this template is only intended to be used as a guideline for author convenience. It is designed for optimum clarity and ease of reading for editors and reviewers, but the template does not reflect the final page layout of a published journal paper. Accepted papers are professionally typeset in XML according to the layout and design of the journal.

>>>>

\begin{abstract}
Abstract
\end{abstract}

% Include a list of up to six keywords after the abstract
\keywords{Geant4, GRB, gamma-rays, satellite, cosmic background}

@@

\section{Introduction}
\label{sect:intro}  % \label{} allows reference to this section
